Modal operators for a constructive account of well quasi-orders

### 2025-06-09 slides-types2025.lagda.tex
Slides as presented this morning

    \pause
    \item Be prepared to evolve approximations (\formalized).

@@

>>>>

    \pause
    \item Be prepared to \hil{evolve approximations} (\formalized).

@@

\addtocounter{framenumber}{-1}
{\renewcommand{\insertframeextra}{c}
\begin{frame}{Stabilization as convenient fiction}
  A commutative ring~$A$ with unit is \ldots
  \begin{itemize}
    \item Noetherian\sinf{} iff for every sequence~$x_0,x_1,\ldots$ of ring elements,
    there is a number~$n : \NN$ such that~$x_n,x_{n+1},x_{n+2},\ldots \in
    (x_0,\ldots,x_{n-1})$.
    \item Noetherian\ensuremath{_\text{RS}} iff for every sequence~$x_0,x_1,\ldots$ of ring elements,
    there is a number~$n : \NN$ such that~$x_n \in
    (x_0,\ldots,x_{n-1})$.
    \item Noetherian\ind{} iff a certain inductively defined condition holds
    [Coquand–Persson].
  \end{itemize}

  We then have:
  \begin{align*}
    \mathsf{Noetherian\ind}(A) &\Longleftrightarrow
    \necessary\mathsf{Noetherian}_\text{RS}(A) \\
    &\Longleftrightarrow
    \necessary\bigl(\badbox{\textsc{lem}} \Rightarrow
    \mathsf{Noetherian}\sinf(A)\bigr) \\
    &\Longleftrightarrow
    \necessary\possible\mathsf{Noetherian}\sinf(A).
  \end{align*}

  Hence, from the corresponding classical proofs, we can extract
  constructive proofs of:
  \begin{enumerate}
    \item Hilbert's basis theorem: If $A$ is Noetherian\ind, then so is $A[X]$.
    \item Locality: If~$1 = f_1+\ldots+f_n$ and if each
    ring~$A[f_i^{-1}]$ is Noetherian\ind, then so is~$A$. \\
    (As a consequence, $A$ is Noetherian\ind
    iff~$\mathcal{O}_{\mathrm{Spec}(A)}$ is.)
  \end{enumerate}
\end{frame}
